---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# grkstyle

<!-- badges: start -->
<!-- badges: end -->

[styler]: https://styler.r-lib.org

`grkstyle` is an extension package for [styler] that holds my personal code style preferences.

## Installation

You can install the grkstyle from Github

``` r
# install.packages("devtools")
devtools::install_github("grkstyle")
```

## Usage

To use `grkstyle` by default in styler functions and addins

```{r eval=FALSE}
# Set default code style for {styler} functions
grkstyle::use_grk_style()
```

Or add the following to your `~/.Rprofile`

```
options(styler.addins_style_transformer = "grkstyle::grk_style_transformer()")
```

## Examples

A few examples drawn from the [tidyverse style guide](https://style.tidyverse.org).

**Unstyled**

```{r, echo=FALSE, results="asis"}
text <- '
do_something_very_complicated(something = "that", requires = many,
                              arguments = "some of which may be long")
'

cat("\n\n``` r", text, "```")
```

**Styled**

```{r, echo=FALSE, results="asis"}
text <- grkstyle::grk_style_text(text)

cat("\n\n``` r", paste(text, collapse = "\n"), "\n```")
```

**Unstyled**

```{r, echo=FALSE, results="asis"}
text <- '
long_function_name <- function(a = "a long argument",
                               b = "another argument",
                               c = "another long argument") {
  # As usual code is indented by two spaces.
}
'

cat("\n\n``` r", text, "```")
```

**Styled**

```{r, echo=FALSE, results="asis"}
text <- grkstyle::grk_style_text(text)

cat("\n\n``` r", paste(text, collapse = "\n"), "\n```")
```

