---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# grkstyle

<!-- badges: start -->
[![grkstyle status badge](https://gadenbuie.r-universe.dev/badges/grkstyle)](https://gadenbuie.r-universe.dev)
<!-- badges: end -->

[styler]: https://styler.r-lib.org

`grkstyle` is an extension package for [styler] that holds my personal code style preferences.

## Installation

You can install grkstyle from my [r-universe](https://gadenbuie.r-universe.dev):

``` r
options(repos = c(
	gadenbuie = "https://gadenbuie.r-universe.dev",
	getOptions("repos")
))

# Download and install grkstyle in R
install.packages("grkstyle")
```

Or you can install grkstyle directly from Github:

``` r
# install.packages("remotes")
remotes::install_github("gadenbuie/grkstyle")
```

## Usage

To use `grkstyle` by default in styler functions and addins

```{r eval=FALSE}
# Set default code style for {styler} functions
grkstyle::use_grk_style()
```

Or add the following to your `~/.Rprofile`

```
options(styler.addins_style_transformer = "grkstyle::grk_style_transformer()")
```

## Examples

A few examples drawn from the [tidyverse style guide](https://style.tidyverse.org).

### Tabs vs Spaces

I've been staunchly committed to indentation by two spaces,
but I've recently come to realize that indentation with tabs is objectively better.
Primarily [it's about accessibility](https://alexandersandberg.com/articles/default-to-tabs-instead-of-spaces-for-an-accessible-first-environment/).
Using tabs allows others to choose their preferred indentation levels,
it accommodates more code authors in a wider variety of scenarios,
and it's better for Braille code readers:

> The main reason I would like to see this change is for refreshable braille displays that are used by blind programmers a lot. Each space wastes one braille cell and takes away valuable braille realestate. So if the default indentation of a project is 4 spaces per level, a 3rd level indentation wastes 12 braille cells before code starts.  
> — [Comment](https://github.com/prettier/prettier/issues/7475#issuecomment-668544890) by [MarcoZehe](https://github.com/MarcoZehe)

**unstyled**

```{r echo = FALSE, results = "asis"}
text_vec <- 'fruits <- c(\n  "apple",\n  "banana",\n  "mango"\n)'
cat("\n``` r", text_vec, "```", sep = "\n")
```

**grkstyle**

```{r, echo=FALSE, results="asis"}
text_vec <- grkstyle::grk_style_text(text_vec)

cat("\n``` r", paste(text_vec, collapse = "\n"), "```", sep = "\n")
```

If you'd like to quickly transition **to tabs** throughout your package code,
you can use the `grk_reindent_tabs_*()` helper functions.
These function apply _only_ the styler indentation rules and should only affect
the indentation of your code.

```r
# re-indent your package code using tabs
grk_reindent_tabs_pkg()
```

There are equivalent helper functions to standardize around spaces,
e.g. `grk_reindent_spaces_*()`.

### Line Breaks Inside Function Calls

**unstyled**

```{r, echo=FALSE, results="asis"}
text <- '
do_something_very_complicated(something = "that", requires = many,
                              arguments = "some of which may be long")
'

cat("\n\n``` r", text, "```")
```

**grkstyle**

```{r, echo=FALSE, results="asis"}
text_grk <- grkstyle::grk_style_text(text)

cat("\n\n``` r", paste(text_grk, collapse = "\n"), "\n```")
```


**styler::tidyverse_style**

```{r, echo=FALSE, results="asis"}
text_tidy <- styler::style_text(text)

cat("\n\n``` r", paste(text_tidy, collapse = "\n"), "\n```")
```

### Indentation of Function Arguments

**unstyled**

```{r, echo=FALSE, results="asis"}
text <- '
long_function_name <- function(a = "a long argument",
                               b = "another argument",
                               c = "another long argument") {
  # As usual code is indented by two spaces.
}
'

cat("\n\n``` r", text, "```")
```

**grkstyle**

```{r, echo=FALSE, results="asis"}
text_grk <- grkstyle::grk_style_text(text)

cat("\n\n``` r", paste(text_grk, collapse = "\n"), "\n```")
```


**styler::tidyverse_style**

```{r, echo=FALSE, results="asis"}
text_tidy <- styler::style_text(text)

cat("\n\n``` r", paste(text_tidy, collapse = "\n"), "\n```")
```



